Commutative Character Sheaves

### 2015-11-13 followup.tex
Starting work on Section 4.

Suppose $G$ is commutative, so $G\der = 1$. 
Suppose $(\cs{L},\mu,\beta)$ is an object in $\CS'(G)$.
Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, and unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find that $\gamma$ is the canonical isomorphism $\xi : m^*\cs{L} \to \theta^*m^*\cs{L}$ coming from the equation $m = m \circ \theta$. 
Thus, when $G$ is commutative, Definition~\ref{def:CCS} recovers Definition~\ref{def:CCScom}.
The next result generalizes this observation.

@@

The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given in Section~\ref{ssec:proofs}, with the proof of Theorem~\ref{thm:Gab}.

@@

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.  We require that $\mu$ be compatible with $\nu$ in the following sense.
We define morphisms:
\begin{align*}
c_0 : H\times G \times G &\to H\times G \times H \times G \\
(h,g_1,g_2) &\mapsto (h,g_1,h,g_2); \\
c_1 : H \times G\times G &\to G\times G \\
(h, g_1, g_2) &\mapsto (hg_1,hg_2); \\
c_2 : H \times G\times G &\to H\times G \\
(h,g_1,g_2) &\mapsto (h, g_1g_2); \\
c_3 : H \times G\times G &\to G\times G \\
(h, g_1, g_2) &\mapsto (g_1, g_2).
\end{align*}
We require that the following diagram of Weil local systems on $H \times G\times G$ commutes:
\begin{equation}\label{ECS1}
\begin{tikzcd}
\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
 & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
\end{tikzcd}
\end{equation}

@@

\subsection{Descent along a torsor}

Now suppose $q : G \to G_0$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G_0.
\end{tikzcd}
\]
Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
Consider the functor
\[
q^* : \CS(G_0) \to \CS(G)
\]
given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{}.
%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
\[
\begin{tikzcd}
a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{rrr}{\nu} & & &  \arrow[equal]{d} p^*\cs{L} \\
a^* ( q^*\cs{L}_0) \arrow{r} 
& (q\circ a)^* \cs{L}_0 \arrow[equal]{r} 
& (q\circ p)^*\cs{L}_0 \arrow{r} 
& p^* (q^*\cs{L}_0)
\end{tikzcd}
\]
Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, arguing as in \cite{cunningham-roe:13a} so $\alpha$ is a morphism in $\CS(G)$.
%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case. It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. I'm just agonizing out loud, I guess.} 
These simple observations define the comparison functor
\[
q_H^* : \CS(G_0) \to CS_H(G)
\]
and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G_0) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]
The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.

@@

We now suppose that $j : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
%Then we have the diagram
%\[
%\begin{tikzcd}
%\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
%G & & G \\
%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
%\end{tikzcd}
%\]
Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
\[
\beta : \cs{L}\vert_H \to (\EE)_{H}
\]
by 
\begin{equation}\label{betanu}
\nu = (\beta \boxtimes \id) \circ  f^*\mu,
\end{equation}
or more precisely, by the following diagram of isomorphisms, where we write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
\[
\begin{tikzcd}
\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The next lemma makes that statement more precise.

@@

\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
Here we use notation from the proof of Proposition~\ref{prop:Gder_triv};
in particular, $H = G\der$.
By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
Since the comparison functor $\CS(G\ab) \to \CS_{H}(G)$ is an equivalence, it determines a full subcategory $\CCS_{H}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{H}(G) \to \CS'(G)$ is $\CCS(G)$.
\[
\begin{tikzcd}[row sep=30]
\CS(H) 
& \arrow{l}[swap]{j^*} \CS(G) 
&\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
&  \CS_{H}(G) \arrow{u}{\text{forget}}  
&  %\arrow[bend left=35pt, dashed]{dll} 
\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}{\text{equiv}} \\
\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}}
& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
& 
\end{tikzcd}
\]

Suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}, as pictured below; 
in particular $\gamma = (q\times q)^* \xi$.
  \[
  \begin{tikzcd}[row sep=10, column sep = 15]
   m_0^*\cs{L}_0 \arrow{dd}[swap]{\xi} \arrow{r}{\mu_0} 
   & \cs{L}_0\boxtimes\cs{L}_0 \arrow{dd}{\vartheta}
&&&   m^*\cs{L} \arrow{dd}[swap]{\gamma} \arrow{r}{\mu} 
 & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}\\
 && \arrow{r}{(q\times q)^*}  &\ & & &\\ 
   \theta^*(m_0^*\cs{L}_0) \arrow{r}{{\theta}^*\mu_0} 
 &  \theta^*(\cs{L}_0\boxtimes\cs{L}_0)
&&&   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} 
&  \theta^*(\cs{L}\boxtimes\cs{L})
  \end{tikzcd}
\]
By Lemma~\ref{lem:HH}, we may interpret the diagram on the right, above, as a diagram in $\Loc_{H\times H}(G\times G)$.
By Lemma~\ref{lem:torsor}, this corresponds to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above, and also that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$.
This completes the proof of Theorem~\ref{thm:Gab}.
%This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
\end{proof}

@@

\section{Applications to supercuspidal representations}

@@

Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$.
We may thus ask for a condition on a commutative character sheaf on $G$ that corresponds to having trivial
trace of Frobenius, with the expectation that the isomorphism classes of such commutative character sheaves
should be in natural bijection with $\Delta^*$.

@@

Let $K$ be a local field with residue field $\Fq$.
Let $\underline{G}$ be a smooth group scheme over $K$.
Set $G_n = \Gr^R_n(\underline{G})$; this is a smooth group scheme over $\Fq$.
Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
Let $\QCS(G)$ be the category of commutative quasicharacter sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.

\begin{proposition}\label{prop:QCS}
$\Hom_\text{cts}(\underline{G}(\OK),\EEx) \iso \QCSiso{G}$.
\end{proposition}

\begin{proof}
\end{proof}

@@

>>>>

Suppose $G$ is commutative, so $G\der = 1$. 
Suppose $(\cs{L},\mu,\beta)$ is an object in $\CS'(G)$.
Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, and unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$. 
 \todo{I'm having some trouble seeing this.}  
Thus, when $G$ is commutative, Definition~\ref{def:CCS} recovers Definition~\ref{def:CCScom}.
The next result generalizes this observation.

@@

The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given in Section~\ref{ssec:proofs}, with the proof of Theorem~\ref{thm:Gab}.
%
Sections~\ref{ssec:equivariant1}, \ref{ssec:equivariant2}, \ref{ssec:descent} and \ref{ssec:closed} set up machinery needed to prove Theorem~\ref{thm:Gab}.

@@

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.  We require that $\mu$ be compatible with $\nu$ in the following sense.
We define morphisms:
\begin{align*}
c_0 : H\times G \times G &\to H\times G \times H \times G \\
(h,g_1,g_2) &\mapsto (h,g_1,h,g_2); \\
c_1 : H \times G\times G &\to G\times G \\
(h, g_1, g_2) &\mapsto (hg_1,hg_2); \\
c_2 : H \times G\times G &\to H\times G \\
(h,g_1,g_2) &\mapsto (h, g_1g_2); \\
c_3 : H \times G\times G &\to G\times G \\
(h, g_1, g_2) &\mapsto (g_1, g_2).
\end{align*}
We require that the following diagram of Weil local systems on $H \times G\times G$ commutes:
\begin{equation}\label{ECS1}
\begin{tikzcd}[column sep=30]
\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
 & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
\end{tikzcd}
\end{equation}

@@

\subsection{Descent along a torsor}\label{ssec:descent}

Now suppose $q : G \to G_0$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G_0.
\end{tikzcd}
\]
Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
Consider the functor
\[
q^* : \CS(G_0) \to \CS(G)
\]
given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
\[
\begin{tikzcd}[column sep=40]
a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
& p^* (q^*\cs{L}_0)
\end{tikzcd}
\]
Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, arguing as in \cite{cunningham-roe:13a} so $\alpha$ is a morphism in $\CS(G)$.
%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case. It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. I'm just agonizing out loud, I guess.} 
These simple observations define the comparison functor
\[
q_H^* : \CS(G_0) \to CS_H(G)
\]
and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G_0) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]
The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.

@@

We now suppose that $j : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
%Then we have the diagram
%\[
%\begin{tikzcd}
%\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
%G & & G \\
%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
%\end{tikzcd}
%\]
Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
\[
\beta : \cs{L}\vert_H \to (\EE)_{H}
\]
by 
\begin{equation}\label{betanu}
\nu = (\beta \boxtimes \id) \circ  f^*\mu,
\end{equation}
or more precisely, by the following diagram of isomorphisms, where we write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
\[
\begin{tikzcd}[column sep=30]
\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The next lemma makes that statement more precise.

@@

\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
Here we use notation from the proof of Proposition~\ref{prop:Gder_triv};
in particular, $H = G\der$.
By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
Since the comparison functor $\CS(G\ab) \to \CS_{H}(G)$ is an equivalence, it determines a full subcategory $\CCS_{H}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{H}(G) \to \CS'(G)$ is $\CCS(G)$.
\[
\begin{tikzcd}[row sep=30, column sep=40]
\CS(H) 
& \arrow{l}[swap]{j^*} \CS(G) 
&\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
&  \CS_{H}(G) \arrow{u}{\text{forget}}  
&  %\arrow[bend left=35pt, dashed]{dll} 
\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}{\text{equiv}} \\
\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}}
& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
& 
\end{tikzcd}
\]

Suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}, as pictured below; 
in particular $\gamma = (q\times q)^* \xi$.
  \[
  \begin{tikzcd}[row sep=10, column sep = 20]
   m_0^*\cs{L}_0 \arrow{dd}[swap]{\xi} \arrow{r}{\mu_0} 
   & \cs{L}_0\boxtimes\cs{L}_0 \arrow{dd}{\vartheta}
&&&   m^*\cs{L} \arrow{dd}[swap]{\gamma} \arrow{r}{\mu} 
 & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}\\
 && \arrow{r}{(q\times q)^*}  &\ & & &\\ 
   \theta^*(m_0^*\cs{L}_0) \arrow{r}{{\theta}^*\mu_0} 
 &  \theta^*(\cs{L}_0\boxtimes\cs{L}_0)
&&&   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} 
&  \theta^*(\cs{L}\boxtimes\cs{L})
  \end{tikzcd}
\]
By Lemma~\ref{lem:HH}, we may interpret the diagram on the right, above, as a diagram in $\Loc_{H\times H}(G\times G)$.
By Lemma~\ref{lem:torsor}, this corresponds to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above, and also that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$.
This completes the proof of Theorem~\ref{thm:Gab}.
%This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
\end{proof}

@@

\section{Applications}

@@

Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$. \todo{Could we turn this into a declared corollary/theorem? It's a nice result.}
We may thus ask for a condition on a commutative character sheaf on $G$ that corresponds to having trivial
trace of Frobenius, with the expectation that the isomorphism classes of such commutative character sheaves
should be in natural bijection with $\Delta^*$.

@@

Let $K$ be a local field with residue field $\Fq$.
Let $\underline{G}$ be a smooth group scheme over $K$.
Set $G_n = \Gr^R_n(\underline{G})$; this is a smooth group scheme over $\Fq$.
Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
Let $\CCS(\underline{G})$ be the category of commutative quasicharacter sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.

\begin{proposition}\label{prop:QCS}
$\underline{G}(\OK)^* \iso \CCSiso{\underline{G}}$.
\end{proposition}

\begin{proof}
That's not correct; it should be 
\[
\CCSiso{\underline{G}} \iso (\Gr(\underline{G})\ab(\Fq))^*.
\]
Is $\Gr(\underline{G})\ab = \Gr(\underline{G}\ab)?$ If so, then at least we get 
\[
\CCSiso{\underline{G}} \iso (\underline{G}\ab(\OK))^*.
\]
\end{proof}

@@

\begin{proposition}
Let $(\underline{G}(\OK),\rho)$ be a type such that  . . . 
Set $G = \Gr(\underline{G})$.
There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) \iso \underline{G}(\OK)$.
\end{proposition}

It is not unique.
